The \project{unRAVE} catalog

### 2016-08-23 article/unrave.tex
Update with proper giturl from vc.tex
Minor text changes about labelled/training set

Throughout this work we adopt the assumptions and nomenclature first set out in
\citet{Ness_2015}, and extended in \citet{Casey_2016b}.  However, one distinction 
here with \citet{Caset_2016} is that in this work the \emph{labelled} set and the
\emph{training} set will be the same set.  In \citet{Casey_2016b} the labelled set
contained two subsets: the training set and a distinct validation set, allowing us
to train on the \emph{training set} and then test on the \emph{validation set}, a 
subset of the labelled set.  However in this work the labelled set is relatively 
small, about an order of magnitude smaller than what was available in 
\citet{Casey_2016b}, and therefore we will use all labelled set stars in the 
training step and supplement our validation experiments with literature comparisons.
Thus, throughout this work we will use the terms \emph{labelled set} and 
\emph{training set} interchangeably.  Below we describe how we constructed the 
training set, before we outline the model that we adopt.

@@

% Refer to the training set figure.
% Two separate models, with an overlap region.
% Worry later about label offsets.

>>>>

Throughout this work we adopt the assumptions and nomenclature first set out in
\citet{Ness_2015}, and extended in \citet{Casey_2016b}.  However, one distinction 
here with \citet{Casey_2016b} is that in this work the \emph{labelled} set and the
\emph{training} set will be the same set.  In \citet{Casey_2016b} two subsets of
the labelled set were defined: the training set and a distinct validation set.
This allowing us to train on the \emph{training set} and then test on the 
\emph{validation set}.  However in this work the labelled set is relatively 
small, about an order of magnitude smaller than what was available in 
\citet{Casey_2016b}, and therefore we will use all labelled set stars in the 
training step and supplement our validation experiments with literature comparisons.
Thus, throughout this work we will use the terms \emph{labelled set} and 
\emph{training set} interchangeably.  Below we describe how we constructed the 
training set, before we outline the model that we adopt.

@@

% Refer to the training set figure.
% Two separate models, with an overlap region.
% Worry later about label offsets.
% Make sure you mention the lack of abundance information in K2/EPIC
